\documentclass[9pt,letterpaper,times]{mtresume}

%===================================================================
% Override default page setup

\geometry{margin=0.7in}

%===================================================================

\name{First Last}
\address{234 Main St.}{Anywhere, CA}{12345}
\phone{123-456-789}
\email{first.last@gmail.com}


\usepackage{lipsum} % for random text use \lipsum

\begin{document}
\maketitle
\thispagestyle{empty} %turn off page numbering


\section*{Experience}

\begin{job}{October 97 to Present}{Deputy Commander, \#\#Operations Group}{USAFB}{%
Supervise and control the daily flying operation, maintenance, support and industrial process for 60 F-16 aircraft. Supervises safe execution of 15,000 sorties annually and all overseas deployments of Wing components. Maintains combat readiness of largest F-16 Wing in the U.S. Oversees the activities of over 1400 personnel and responsible for \$4 billion worth of assets. Certified F-16C Instructor Pilot (IP).
}
\accomplishment Noted on performance evaluation as ``best Lieutenant Colonel in 388th Wing'' out of 20 by General Officer Wing Commander.
\accomplishment Maintained highest F-16 combat readiness rates in entire U.S., fully 5\% higher than any like Wing.
\accomplishment Noted for role in assisting one squadron in achieving 95\% survival rate at Red Flag, versus average of only 50\%.
\end{job}

\begin{job}{June 96 to September 97}{Deputy Commander, \#\#Support Operations Group}{USAB}{%
Responsible for entire Air base infrastructure, to include facilities, communications, disaster response, fire rescue, explosive ordnance disposal, family housing,
security, retail sales, and personnel services. Supervised over 2,000 personnel. Controlled \$75 million operation and maintenance
budget, and oversaw \$240 million worth of ongoing construction projects.
}
\accomplishment Recognized on performance evaluation as having done ``more for the wing than any other LTC'' of 50 by Wing Commander.
\accomplishment Base won 1997 Air Force Installation of the Year Award.
\accomplishment Base won 1996 U.S. Air Forces Europe (USAFE) Installation of the Year Award.
\end{job}

\begin{job}{June 95 to June 96}{Chief, Wing Readiness, \#\#Fighter Wing}{}{%
Designed, executed and evaluated all local exercises in preparation
for real world deployment contingencies. Supervised 200 personnel responsible for preparing and evaluating NATO inspection
readiness. Oversaw all preparations for NATO Tactical Evaluation, USAF Operational Readiness Inspection, USAF Nuclear Surety
Inspections and Conventional Forces Europe (CFE) Inspections. Certified F-16C IP.
}
\accomplishment Noted as being in ``Top 1\% of officers in Air Force'' and ``most versatile officer in wing (out of 200)'' on performance evaluation.
\accomplishment Recognized by Wing Commander as being directly responsible for combat readiness of USAFE's largest and most diverse wing.
\accomplishment Personally selected by Supreme Allied Commander Europe to lead operational inspection of Operation Provide Comfort in Turkey
after shootdown of 2 helicopters.
\end{job}

\begin{job}{May 92 to June 95}{Assistant Operations Officer, \#\# Fighter Squadron}{USAFB}{%
Responsible for overseeing squadron
utilization of 4,800 annual sorties and 6,000 flying hours pursuant to maintaining squadron flying and deployment readiness.
Supervised all maintenance scheduling activities.
}
\accomplishment Maintained highest combat readiness rate of any squadron in entire Air Force.
\accomplishment Achieved unprecedented 100\% sortie effectiveness and sortie scheduling effectiveness rates.
\accomplishment Squadron awarded USAFE Maintenance Effectiveness Award for best maintenance in entire command.
\end{job}

\begin{job}{May 91 to May 92}{Executive Officer to Chief of Staff for Plans, Headquarters Air Command}{}{%
Managed administrative
processes and support for Deputy Chief of Staff for Plans [DCS(P)], a US Air Force Major General, who directed all long range
strategic planning (including the elimination of SAC and TAC) for a command of 190,000 personnel equipment valued at over \$49
billion. Resource advisor for an administrative operating budget of \$800,000.
}
\accomplishment Noted by DCS(P) as being ``the most competent officer out of 400'' in the Plans Directorate, on annual evaluation.
\accomplishment Achieved largest-ever recorded increase in Directorate productivity by designing and creating a Microsoft software school.
\end{job}

\begin{job}{August 89 to May 91}{Aircraft Program Manager, Headquarters Air Command}{}{%
Responsible for developing relocation plans
consistent with base closures and procured funding for all aircraft modifications. Responsible for the support and movement of over
400 fighter and support aircraft throughout this worldwide command.
}
\accomplishment Handpicked to plan and execute the Air Force's first-ever implementation of a ``Composite Wing'' combining diverse aircraft type
under one Wing Commander: chaired a 150-person working group and supervised \$66 million start-up budget.
\accomplishment Developed FB-111 movement plan approved by Congress that saved Air Force over \$479 million in operational/support costs.
\accomplishment Incorporated novel housing ``lease'' plan in FB-111 move, eliminating regulatory 4-year timeline for major military construction.
\end{job}

\begin{job}{May 83 to August 89}{Flight Commander and Instructor Pilot}{}{%
Responsible for the combat employment of F-111E aircraft and
professional development of 12 aircrew members supporting both NATO and US nuclear and conventional tasking. Responsible for
planning and executing long range contingency operations. Mission ready instructor pilot in the F-111E aircraft.
}
\accomplishment Rated ``excellent'' on all 20 missions led during NATO Tactical evaluation.
\accomplishment Led squadron to an ``outstanding'' (highest rating given) rating on two NATO Tactical Evaluations---first in NATO history.
\accomplishment Saved Wing 1,122,000 man-hours per year without reducing combat capability by changing one headquarters regulation.
\accomplishment Recognized as ``Best'' mission commander in wing (out of over 100 pilots).
\end{job}


\section*{Education}

\begin{degree}{MA Business Administration}{1982}{Central Gridiron University}{Seol, South Korea}\end{degree}
\begin{degree}{BS Business Management}{1978}{University of Northern California}{Santa Rosa, CA}\end{degree}

\end{document}

